Modeling the Linux page cache for accurate simulation of data-intensive applications

### 2020-12-18 paper_io_sim.tex
Edits in concurrent experiment

\newcommand{\tristan}[1]{}%\color{orange}\textbf{From Tristan:}#1\color{black}}
\newcommand{\henri}[1]{\color{green}\textbf{From Henri:}#1\color{black}}
\newcommand{\english}[1]{\uwave{#1}}

@@

            The page cache model notably reduced \wrench's simulation error
            for concurrent applications executed with local I/Os
            (Figure~\ref{fig:multi_local}). For reads, \wrench-cache still
            slightly overestimated reality, due to the discrepancy between
            simulated and real read bandwidths mentioned before. For writes,
            \wrench-cache slightly underestimated reality for the same reason. The plateau
            ending around 7 concurrent applications in the \wrench-cache writes
            marks the limit beyond which the page cache was saturated with dirty data
            and needed flushing. \tristan{why is there no plateau in real life?}

>>>>

\newcommand{\tristan}[1]{\color{orange}\textbf{From Tristan:}#1\color{black}}
\newcommand{\henri}[1]{\color{green}\textbf{From Henri:}#1\color{black}}
\newcommand{\english}[1]{\uwave{#1}}

@@

            The page cache model notably reduced \wrench's simulation error
            for concurrent applications executed with local I/Os
            (Figure~\ref{fig:multi_local}). For reads, \wrench-cache still
            slightly overestimated reality, due to the discrepancy between
            simulated and real read bandwidths mentioned before. For
            writes, \wrench-cache correctly retrieves the plateau ending at
            \tristan{x} concurrent applications in real life, corresponding
            to the limit beyond which the page cache was saturated with
            dirty data and needed flushing.
